---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  dpi = 300
)
```

# geoidep

<img src="man/figures/geoidep.svg" align="right" hspace="10" vspace="0" width="20%">

<!-- badges: start -->
[![R-CMD-check](https://github.com/ambarja/geoidep/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/ambarja/geoidep/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/ambarja/geoidep/graph/badge.svg)](https://app.codecov.io/gh/ambarja/geoidep)
<!-- badges: end -->

The goal of geoidep is to offers R users an easy and accessible way to obtain official cartographic data on various topics, such as society, transport, environment, agriculture, climate, among others.

It also includes information provided by regional government entities and technical-scientific institutions,managed by the Spatial Data Infrastructure of Peru.

## Installation

You can install the development version of geoidep like so:

```r
install.packages('pak')
pak::pkg_install("ambarja/geoidep")
```

## Example

This is a simple example of how to download Peru's official administrative boundaries:

```{r}
library(geoidep)
```


```{r example}
dep <- get_departaments(show_progress = FALSE)
```

The first 10 rows of the original data are displayed here:
```{r dep}
head(dep)
```
