---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/fig-",
  out.width = "100%",
  dpi = 300
)
```

# geoidep

<img src="man/figures/geoidep.svg" align="right" hspace="10" vspace="0" width="22%">

<!-- badges: start -->
[![R-CMD-check](https://github.com/ambarja/geoidep/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/ambarja/geoidep/actions/workflows/R-CMD-check.yaml)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![Codecov test coverage](https://codecov.io/gh/ambarja/geoidep/graph/badge.svg)](https://app.codecov.io/gh/ambarja/geoidep)
<!-- badges: end -->

The goal of **geoidep**ðŸ“¦ is to offers R users an easy and accessible way to obtain official cartographic data on various topics, such as **society** ðŸ›ï¸, **transport**ðŸš—, **environment**ðŸŒ±, **agriculture**ðŸŒ¾, **climate**â›…ï¸,among others.

This includes information provided by regional government entities and technical-scientific institutions, managed by the **Spatial Data Infrastructure of Peru**.

## Installation

You can install the development version of geoidep like so:

```r
install.packages('pak')
pak::pkg_install('ambarja/geoidep')
```

or also the official version available on CRAN:

```r
install.packages('geoidep')
```


## Example 01: Introduction

```{r}
library(geoidep)
```

In this example, we can identify the list of providers available in geoidep and the layers they present.

```{r}
get_data_sources() |> 
  head()
```
In summary the suppliers and the number of available layers

```{r}
get_providers() 
```

## Example 02: Download official INEI administrative boundaries

This is a simple example of how to download Peru's official administrative boundaries:

```{r}
dep <- get_departaments(show_progress = FALSE)
```

The first 10 rows of the original data are displayed here:
```{r}
head(dep)
```
